Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

model_5 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

>>>>

model_5 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (1 | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 3, iter = 100*2
)
```

@@

```{r}
#set.seed(454)
my_data <- data.frame(StateColor = "red", State = "FL")

# Simulate a set of predictions for each case in newdata
my_prediction <- posterior_predict(
 model_5,
  newdata = my_data)
